Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-14 ms.tex
caption for full-sky results figure

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{\label{fig:results} Our best-fit $T_2$, binned to 27.5$'$ resolution}
\end{center}
\end{figure*}

@@

% CIBA
The CIBA remains a major imperfection that still requires further 
investigation. The CIB anisotropies are very evident in low-dust regions of our
maps of optical depth and predicted dust emission. As described in 
$\S$\ref{sec:mcmc}, we have propagated the CIBA RMS amplitudes and 
inter-frequency covariances into our uncertainty estimates through the 
likelihood function in our MCMC procedure. However, this treatment falls far 
short of actually removing the spatial imprint of the CIBA on our optical depth
and temperature maps. The CIB anisotropies are more prominent in our optical 
depth map relative to that of SFD because of the lower-frequency \PLANCK~maps 
we rely upon to achieve a high-resolution temperature correction.

>>>>

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our 
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD 
\texttt{i100}, downbinned to 27.5$'$ resolution. (bottom) Corresponding
full-sky map of best-fit 545 GHz optical depth.}
\end{center}
\end{figure*}

@@

% CIBA
The CIBA remains a major imperfection that still requires further 
investigation. The CIB anisotropies are very evident in low-dust regions of our
maps of optical depth and predicted dust emission. As described in 
$\S$\ref{sec:mcmc}, we have propagated the CIBA RMS amplitudes and 
inter-frequency covariances into our uncertainty estimates through the 
likelihood function in our MCMC procedure. However, this treatment falls far 
short of actually removing the spatial imprint of the CIBA on our derived 
parameters. The CIB anisotropies are more prominent in our optical depth map 
relative to that of SFD because of the lower-frequency \PLANCK~maps we rely 
upon to achieve a high-resolution temperature correction.
